---
title: "Testing distill article CSS"
description: |
  A new article created using the Distill format.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_float: false
    css: [variables.css, base-style.css]
creative_commons: CC BY
repository_url: https://github.com/apreshill/distill-css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sass)
```


## Style here

```{sass eval=FALSE}
$body-bg: red;
body{
  background-color: $body-bg;
}

```

## Text here

Distill is a publication format for scientific and technical writing, native to the web. 

Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.


<aside>You won't have to use GitHub for the session, but many of tools we'll use integrate nicely with version control via GitHub. To get started, complete these [installation instructions](https://happygitwithr.com/install-intro.html), then test your connection between GitHub and RStudio following [these steps](https://happygitwithr.com/connect-intro.html).^[We *strongly recommend* that if you are not already a fluent GitHub user you choose [HTTPS over SSH](https://happygitwithr.com/credential-caching.html).]. </aside>


## Code here

```{r}
library(palmerpenguins)
library(tidyverse)
penguins %>% 
  filter(year == 2007 & species == "Gentoo") %>% 
  summarise(mean_fl = mean(flipper_length_mm, na.rm = TRUE))
```

